Towards Verifying the Bitcoin-S Library

### 2019-06-26 paper/paper.tex
change titles

\subsection{Turning Object into Case Object}

@@

\subsection{Getting Rid of Abstract Type Member}

@@

\subsection{Replacing the BigInt Constructor Argument With A String Literal}

@@

\subsection{Getting Rid of Special Generics}

@@

\subsection{Removing toLong}

Stainless output:
\begin{lstlisting}[style=stainless]
[ Error  ] number/NumberType.scala:14:22: Unknown call to bigInteger on Number.this.toBigInt (BigInt) with arguments List() of type List()
            def toLong: Long = toBigInt.bigInteger.longValueExact()
                              ^^^^^^^^^^^^^^^^^^^
\end{lstlisting}

@@

\subsection{Getting Rid of Concrete Type}

@@

\subsection{Replacing the BigInt \&-Function With Bound Check}
\label{sec:bound_check}

@@

\subsection{Extracting Private Inner Classes}

@@

\subsection{Removing Second Parameter of Require}

@@

\subsection{Rewriting BigInt to Long Conversions}

@@

>>>>

\subsection{An Inheriting Object}

@@

\subsection{Abstract Type Member}

@@

\subsection{Non-Literal BigInt Constructor Argument}

@@

\subsection{Self-Reference in Type Parameter Bound}

@@

\subsection{Missing Member \texttt{bigInteger} in BigInt}
\todo{Ramon is .bigInteger missing in Stainless?}
Stainless output:
\begin{lstlisting}[style=stainless]
[ Error  ] number/NumberType.scala:14:22: Unknown call to bigInteger on Number.this.toBigInt (BigInt) with arguments List() of type List()
            def toLong: Long = toBigInt.bigInteger.longValueExact()
                              ^^^^^^^^^^^^^^^^^^^
\end{lstlisting}

@@

\subsection{Type Member}

@@

\subsection{Missing Bitwise-And Method on BigInt}
\label{sec:bound_check}

@@

\subsection{Inner Class in Case Object}

@@

\subsection{Message Parameter in Require}

@@

\subsection{Missing Implicit Long to BigInt Conversion}

@@

\subsection{Missing BigInt Constructor with Long Argument}
\todo{Split code from above}
